Diagnoses and cell types

### 2025-08-21 analyses/infercnv-consensus-cell-type/exploratory-notebooks/reference-query-counts.Rmd
Update analyses/infercnv-consensus-cell-type/exploratory-notebooks/reference-query-counts.Rmd
Co-authored-by: Ally Hawkins <54039191+allyhawkins@users.noreply.github.com>
keep multiplexed, and save intermediate dataframe for math

```{r}
sample_diagnosis_df <- metadata_files |>
  purrr::map(
    \(file) {
      readr::read_tsv(file) |>
        # don't consider multiplexed or cell line
        dplyr::filter(!is_multiplexed, !is_cell_line) |>
        dplyr::select(contains("scpca"), diagnosis)
  }) |>
  dplyr::bind_rows() |>
  # use inner_join to remove normals
  dplyr::inner_join(diagnosis_map, by = c("diagnosis" = "submitted_diagnosis")) |>
  dplyr::select(-ontology_id, -human_readable_value)
```

@@

```{r}
sum(sample_counts_df$reference >= params$n_reference_threshold) / nrow(sample_counts_df)
```

@@

There is one project about 7x as many reference as query cells; let's look more closely:

>>>>

```{r}
all_sample_diagnosis_df <- metadata_files |>
  purrr::map(
    \(file) {
      readr::read_tsv(file) |>
        dplyr::select(contains("scpca"), diagnosis, is_cell_line, is_multiplexed)
  }) |>
  dplyr::bind_rows() |>
  # use inner_join to remove normals
  dplyr::inner_join(diagnosis_map, by = c("diagnosis" = "submitted_diagnosis")) |>
  dplyr::select(-ontology_id, -human_readable_value)

total_samples <- nrow(all_sample_diagnosis_df) # needed for later math

sample_diagnosis_df <- all_sample_diagnosis_df |>
  # don't consider cell line (or multiplexed?)
  # for now at least, we are retaining multiplexed
  dplyr::filter(!is_cell_line)
```

@@

```{r}
sum(sample_counts_df$reference >= params$n_reference_threshold) / total_samples
```

@@

There is one library with about 7x as many reference as query cells; let's look more closely:
